Asymmetric relationships and their effects on coexistence

### 2023-08-02 paper/Paper.Rnw
acknowledgements

The authors thank Shyamolina Ghosh for suggesting the research problem, and Lawrence Sheppard, Max Castorani,
Jon Walter, Jude Kastens, Vadim Karatayev, Emily Arsenault, Jordan Rodriguez, Lauren Hallett, 
Robin Snyder, and three anonymous referees and the editor for helpful feedback. 
The authors especially thank Steve Ellner for key advice at several watershed moments in the development of the project. 
The authors were partly supported by US National
Science Foundation grants 1714195 and 2023474, the James S McDonnell Foundation, the California Department of Fish and
Wildlife Delta Science Program, and the Alexander von Humboldt Foundation.

>>>>

The authors thank Shyamolina Ghosh for suggesting the research problem, and Lawrence Sheppard, Max Castorani,
Jon Walter, Jude Kastens, Vadim Karatayev, Emily Arsenault, Jordan Rodriguez, Lauren Hallett, 
Madelon Case, Chhaya Werner, Lina Aoyama, Steven Haring, Carmen Watkins,
Robin Snyder, and three anonymous referees and the editor for helpful feedback. 
The authors especially thank Steve Ellner for key advice at several watershed moments in the development of the project. 
The authors were partly supported by US National
Science Foundation grants 1714195 and 2023474, the James S McDonnell Foundation, the California Department of Fish and
Wildlife Delta Science Program, and the Alexander von Humboldt Foundation.
